### 2018-03-29 latex/sc18/prelims.tex
software environment details
finished pass through performance section
changed algorithm in prelims to use R instead of k
finished conclusion

A Nonnegative CP decomposition (NNCP) constrains the factor matrices to have nonnegative values.
In this work, we are interested in NNCP models that are good approximations to $\TA$ in the least squares sense.
That is, we seek to minimize $\|\TA-\CPl\|$, where the tensor norm is a generalization of the matrix Frobenius or vector 2-norm, the square root of the sum of squares of the entries.

@@

\SplitN{\label{eqn:bcdnncp}}{
\HH^{(n)} \leftarrow \argmin_{\HH \geq 0} & \| \Mn{S}{n} \HH^T - \Mn{M}{n}^T \|_F^2
}

>>>>

A Nonnegative CP decomposition (NNCP) constrains the factor matrices to have nonnegative values.
In this work, we are interested in NNCP models that are good approximations to $\TA$ in the least squares sense.
That is, we seek 
$$\min_{\HH^{(i)} \geq 0}  \| \TA - \CPl \|,$$
where the tensor norm is a generalization of the matrix Frobenius or vector 2-norm, the square root of the sum of squares of the entries.

@@

%\SplitN{\label{eqn:bcdnncp}}{
$$\HH^{(n)} \leftarrow \argmin_{\HH \geq 0}  \| \Mn{S}{n} \HH^T - {\Mn{M}{n}}^T \|_F^2$$
%}
